---
 title: "CRC work"
 author: "Taylor"
 date: "9/22/2017"
 output: html_document
 ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("rmarkdown")
library(rmarkdown)
#library(BiocLite)
#install.packages("genelib")
#library(genefilter)
#install.packages("genefilter")

options(stringsAsFactors = FALSE)
```

## R Markdown
 This is the basic file format for the for loop I will be runnin g on each table the make sure that there is a 
  files <- list.files(path="path/t", pattern="*.txt", full.names=T, recursive=FALSE)
  lapply(files, function(x) {
    t <- read.table(x, header=F) # load file
    # apply function
   
    out <- function(t)
      # write to file
      write.table(out, "path/to/output", sep="\t", quote=F, row.names=F, col.names=T)
  })
#Begin work here
The first thing was to create a list of all the genes mutated in a specific pattern
Started with samples passed by Somatic Mutation caller using MuTect_2
Then greped each file for the SNV mutations
after that seperated for impact from High to low or Modifier
```{r}
files_snvh <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVHIGH.txt", full.names=T, recursive=FALSE)
  lapply(files_snvh, function(x){
  # print(basename)
    filename <- x
    #basename <- gsub(".*/Volumes/home/greally-lab/T_Trial/Tables/", "", filename)
    #colnames(y) <-("counts", basename)
    if(file.size(x)>0){
        t <- read.table(x, header=F)
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      print(blue_genes)
      write.table(out, "out_snvh.txt", append = TRUE, sep="\t", na ="NA", quote=F, col.names= tools::file_path_sans_ext(basename(filename)))
        }
    })
```
#Create genelist from input information
```{r}
butt = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_3.txt", header = F)
#butt_3 <- read.delim("out_snvh.txt", header = F)
genes <- as.matrix(butt$V2[!duplicated(butt$V2)]) 
genelist <- as.matrix(sort(genes))
#removed the first empty row
genelist <- as.matrix(sort(genes[2:length(genes)]))
colnames(genelist) <- c("GENES")
dim(genelist)
write.csv(genelist, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.csv")
saveRDS(file, file = "/Volumes/home/greally-lab/T_Trial/Tables/file.Rds")
saveRDS(genelist, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
```
#for each file read in the file, loop for column 2 in genelist, if the names match output file column 1, else output 0
SNVHigh Pass is the test directory
Repeat the code for all other modifier patterns
```{r}
#SNV MODIFIER
files_snvm <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVMOD.txt", full.names=T, recursive=FALSE)
toy_snvm <- files_snvm[1:10]
lapply(files_snvm, function(x){
    if(file.size(x)>0){
      t <- read.table(x, header=F, fill = TRUE)
      #some files have blanks so have to remove the blanks
        if(t[1,2] == ""){
          t <- t[2:nrow(t),]
        }
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      #print(blue_genes)
      write.table(out, "/Volumes/home/greally-lab/T_Trial/Tables/out_snvm.txt", append = TRUE, sep="\t", na ="NA", quote=F,col.names= tools::file_path_sans_ext(basename(x)))
        }
})
#Creating the list of genes
butt = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_snvm.txt", header = F)
genes_snvm <- as.matrix(butt$V2[!duplicated(butt$V2)]) 
#genelist_snvm <- as.data.frame(sort(genes_snvm[2]))
head(genes_snvm)
#removed the first empty row
genelist_snvm <- as.matrix(sort(genes_snvm[2:length(genes_snvm)]))
colnames(genelist_snvm) <- c("GENES")
head(genelist_snvm)
#write.csv(genelist_snvm, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvm.csv")
#Saving the varables
saveRDS(files_snvm, file = "/Volumes/home/greally-lab/T_Trial/Tables/files_snvm.Rds")
saveRDS(genelist_snvm, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvm.Rds")



#SNVLOW
files_snvl <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVLOW.txt", full.names=T, recursive=FALSE)
toy_snvl <- files_snvl[1:10]
lapply(files_snvl, function(x){
    if(file.size(x)>0){
      t <- read.table(x, header=F, fill = TRUE)
      #some files have blanks so have to remove the blanks
        if(t[1,2] == ""){
          t <- t[2:nrow(t),]
        }
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      #print(blue_genes)
      write.table(out, "/Volumes/home/greally-lab/T_Trial/Tables/out_snvl.txt", append = TRUE, sep="\t", na ="NA", quote=F,col.names= tools::file_path_sans_ext(basename(x)))
        }
})
#Creating the list of genes
butt_snvl = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_snvl.txt", header = F)
genes_snvl <- as.matrix(butt_snvl$V2[!duplicated(butt_snvl$V2)]) 
#genelist_snvl <- as.data.frame(sort(genes_snvl[2]))
head(genes_snvl)
#removed the first empty row 
#MAKE SURE THIS WORKS
genelist_snvl <- as.matrix(sort(genes_snvl[2:length(genes_snvl)]))
dim(genelist_snvl)
colnames(genelist_snvl) <- c("GENES")
head(genelist_snvl)
#write.csv(genelist_snvl, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvl.csv")
#Saving the varables
saveRDS(files_snvl, file = "/Volumes/home/greally-lab/T_Trial/Tables/files_snvl.Rds")
saveRDS(genelist_snvl, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvl.Rds")

#INDEL HIGH
files_IDH <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pINDELHIGH.txt", full.names=T, recursive=FALSE)
toy_IDH <- files_IDH[1:10]
lapply(files_IDH, function(x){
    if(file.size(x)>0){
      t <- read.table(x, header=F, fill = TRUE)
      #some files have blanks so have to remove the blanks
        if(t[1,2] == ""){
          t <- t[2:nrow(t),]
        }
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      #print(blue_genes)
      write.table(out, "/Volumes/home/greally-lab/T_Trial/Tables/out_IDH.txt", append = TRUE, sep="\t", na ="NA", quote=F,col.names= tools::file_path_sans_ext(basename(x)))
        }
})
#Creating the list of genes
butt = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_IDH.txt", header = F)
genes_IDH <- as.matrix(butt$V2[!duplicated(butt$V2)]) 
#genelist_IDH <- as.data.frame(sort(genes_IDH[2]))
head(genes_IDH)
#removed the first empty row
genelist_IDH <- as.matrix(sort(genes_IDH[2:length(genes_IDH)]))
colnames(genelist_IDH) <- c("GENES")
head(genelist_IDH)
#write.csv(genelist_IDH, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDH.csv")
#Saving the varables
saveRDS(files_IDH, file = "/Volumes/home/greally-lab/T_Trial/Tables/files_IDH.Rds")
saveRDS(genelist_IDH, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDH.Rds")

#INDEL LOW
files_IDL <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pINDELLOW.txt", full.names=T, recursive=FALSE)
toy_IDL <- files_IDL[1:10]
lapply(files_IDL, function(x){
    if(file.size(x)>0){
      t <- read.table(x, header=F, fill = TRUE)
      #some files have blanks so have to remove the blanks
        if(t[1,2] == ""){
          t <- t[2:nrow(t),]
        }
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      #print(blue_genes)
      write.table(out, "/Volumes/home/greally-lab/T_Trial/Tables/out_IDL.txt", append = TRUE, sep="\t", na ="NA", quote=F,col.names= tools::file_path_sans_ext(basename(x)))
        }
})
#Creating the list of genes
butt = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_IDL.txt", header = F)
genes_IDL <- as.matrix(butt$V2[!duplicated(butt$V2)]) 
#genelist_IDL <- as.data.frame(sort(genes_IDL[2]))
head(genes_IDL)
#removed the first empty row
genelist_IDL <- as.matrix(sort(genes_IDL[2:length(genes_IDL)]))
colnames(genelist_IDL) <- c("GENES")
head(genelist_IDL)
#write.csv(genelist_IDL, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDL.csv")
#Saving the varables
saveRDS(files_IDL, file = "/Volumes/home/greally-lab/T_Trial/Tables/files_IDL.Rds")
saveRDS(genelist_IDL, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDL.Rds")

#INDEL MODIFIER  GENE LIST
files_IDM <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pINDELMOD.txt", full.names=T, recursive=FALSE)
toy_IDM <- files_IDM[1:10]
lapply(files_IDM, function(x){
    if(file.size(x)>0){
      t <- read.table(x, header=F, fill = TRUE)
      #some files have blanks so have to remove the blanks
        if(t[1,2] == ""){
          t <- t[2:nrow(t),]
        }
      blue_genes <-as.vector(t$V2) 
      out <- blue_genes[!duplicated(blue_genes)]
      #print(blue_genes)
      write.table(out, "/Volumes/home/greally-lab/T_Trial/Tables/out_IDM.txt", append = TRUE, sep="\t", na ="NA", quote=F,col.names= tools::file_path_sans_ext(basename(x)))
        }
})
#Creating the list of genes
butt = read.delim("/Volumes/home/greally-lab/T_Trial/Tables/out_IDM.txt", header = F)
genes_IDM <- as.matrix(butt$V2[!duplicated(butt$V2)]) 
#genelist_IDM <- as.data.frame(sort(genes_IDM[2]))
head(genes_IDM)
#removed the first empty row
genelist_IDM <- as.matrix(sort(genes_IDM[2:length(genes_IDM)]))
colnames(genelist_IDM) <- c("GENES")
head(genelist_IDM)
#write.csv(genelist_IDM, "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDM.csv")
#Saving the varables
saveRDS(files_IDM, file = "/Volumes/home/greally-lab/T_Trial/Tables/files_IDM.Rds")
saveRDS(genelist_IDM, file = "/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDM.Rds")
```
```{r MASTER Gene list}
genelist_snvh <- readRDS("/Volumes/home/greally-lab/T_Trail/Tables/genelist_snvh.Rds")
genelist_snvl <- readRDS("/Volumes/home/greally-lab/T_Trail/Tables/genelist_snvl.Rds")
genelist_snvm <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvm.Rds")
genelist_IDH <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDH.Rds")
genelist_IDL <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDL.Rds")
genelist_IDM <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_IDM.Rds")

full_gene_list <- rbind(genelist_snvh, genelist_snvl, genelist_snvm, genelist_IDM,genelist_IDH, genelist_IDL)
full_gene_list <- full_gene_list[!duplicated(full_gene_list)]
full_gene_list <- as.data.frame(full_gene_list)
colnames(full_gene_list) <- c("GENES")
head(full_gene_list)
saveRDS(full_gene_list,file = "/Volumes/home/greally-lab/T_Trial/Tables/full_genelist.Rds")

```
```{r}
#first atttempt Code 
files <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVHIGH.txt", full.names=T, recursive=FALSE)
  
    #set table once then run it
genelist_snvh <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
        #snv_table_f <-as.data.frame(genelist)
        #snvh_temp <- as.data.frame(cbind(genelist,0))
col<- length(files)
ro <- length(genelist_snvh)
    snvh_list <- data.frame()
    snvh_table <- data.frame(nrow = ro,ncol = col)
    tab<- matrix(nrow = ro, ncol = 1)
    #snvh_tab is a table that will be changed each time I should define it out of the bounds of the loop
snvh_tab <- as.data.frame(rep(0,ro), row.names =genelist_snvh) 
    
 
    base <- list()
    #named <- list()
    # tried doing a for loop instead of lapply
  for(j in 1:length(toy)){
    # This is doing hte same thing it was doing when I put it at the end. It goes 1, then ,1,2, then 1,2,3 instead of 1. 2. 3. 
      fil <- toy[j]
      #creating variables to include the names of each patient along with each table read in. If not I can make this a vectore for later table naming
      base[j] <- tools::file_path_sans_ext(basename(fil))
      named[j] <- c("counts",base[j])
      #if the file is larger than 0 read in the file as a table with 2 columns, column 1 is the counts, column 2(V2) are the gene names
        if (file.size(fil)>0){
          tab <- read.table(fil, header=F)
          View(tab)
          print(paste0(base,"is greater than 0"))
          #Check to see which are greater than 0
            gene<-tab$V2
            counts<-tab$V1
            #Checkpoint to print out genes and counts for each
            print(gene)
            print(counts)
            #created a temparary column that was full of zeros
            #created temporary table for matching
        }
  }
            temp_col <- as.data.frame(rep(0,6645))
            snvh_temp <-cbind(genelist_snvh,0)
                for (i in 1:length(gene)){
                  match <- charmatch(gene[i],genelist)
                  print(match)
                  snvh_temp[match,2] <- counts[i]
                }
            temp_col <- snvh_temp[,2]
              #temp_col[match] <- counts[i]
              #View(temp_col)
            snvh_tab <- merge(snvh_tab,temp_col)
            View(snvh_tab)
        }
      else{
      #otherwise temp-col should just be a bunch of zeros
      temp_col <- as.data.frame(rep(0,6645))
      snvh_tab <- merge(snvh_tab,temp_col) 
      #}
      }
  }
```

```{r}
files_snvh <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVHIGH.txt", full.names=T, recursive=FALSE)
toy_2 <- files[1:10]
ten <- files[10]
options(stringsAsFactors = FALSE)
genelist_snvh <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
full_gene_list <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/full_genelist.Rds")
#snvh_tab <- as.data.frame(rep(0,ro), row.names =genelist_snvh)
#defining Temp outside of the function to prevent it's repeated emptying
temp <- full_gene_list
snvh_tabl <- temp

for (i in 1:length(files_snvh)) {
  x<- files_snvh[i]
  base <- tools::file_path_sans_ext(basename(x))
  base <- gsub("_pSNVHIGH","",base)
  named <- c(base,"genes")
   if (file.size(x)>0){
    #print(named)
    #save each table as a rds then red it back in as a dataframe with column names
    mini_table <- read.table(x, header =FALSE)
    colnames(mini_table) <- named
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    #saveRDS(column,file = "/Volumes/home/greally-lab/T_Trial/Work/")
    #write.table(column,file = "/Volumes/home/greally-lab/T_Trial/Work/columns_3.txt", sep = "\t", append = TRUE, col.names = TRUE)
    snvh_tabl <- merge(snvh_tabl, column, by="GENES", all=TRUE)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    #View(column)
    #write.table(column, file = "/Volumes/home/greally-lab/T_Trial/Work/columns_3.txt", sep = "\t", append = TRUE, col.names = TRUE)
    snvh_tabl <- merge(snvh_tabl, column, by="GENES", all=TRUE)
  #View(snvh_tabl)
  }
}
saveRDS(snvh_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/snvh_table_full.Rds")
snvh_table <-readRDS("/Volumes/home/greally-lab/T_Trial/Tables/snvh_table.Rds")
snvh_table_full <-readRDS("/Volumes/home/greally-lab/T_Trial/Tables/snvh_table_full.Rds")
head(snvh_tabl, 10)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(snvh_tabl[,3])))
#check that the 1s are in the correct place
snvh_tabl[which(snvh_tabl[,3]==1),]
class(snvh_tabl)
snvh_tabl <- as.data.frame(snvh_tabl)
```
#Repeat the script for each table needed to make
The SNVM files may have and empty 1st column so I needed to delete them
Not sure why they were empty
This code took forever. Need to find a new way to do this the 
```{r}
#Making the table
options(stringsAsFactors = FALSE)
files_snvm <- list.files(path="/Volumes/home/greally-lab/T_Trial/Tables", pattern="*_pSNVMOD.txt", full.names=T, recursive=FALSE)
genelist_snvm <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvm.Rds")
#snvm_tabl <- as.data.frame(rep(0,nrow(genelist_snvm)), row.names =genelist_snvm)
toy_snvm <-files_snvm[1:10]
#defining Temp outside of the function to prevent it's repeated emptying
temp <- genelist_snvm
snvm_tabl <- temp
x <- files_snvm[2]
for (i in 1:length(files_snvm)){
  x<- files_snvm[i]
  base <- tools::file_path_sans_ext(basename(x))
  base <- gsub("_pSNVMOD","",base)
  named_snvm <- c(base,"genes")
   if (file.size(x)>0){
    #print(named)
    #save each table as a rds then red it back in as a dataframe with column names
    mini_table <- read.table(x, header =FALSE, fill = TRUE)
    if(mini_table[1,2] == ""){
          mini_table <- mini_table[2:nrow(mini_table),]
        }
    colnames(mini_table) <- named_snvm
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    snvm_tabl <- merge(snvm_tabl, column, by="GENES", all=TRUE)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named_snvm
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    snvm_tabl <- merge(snvm_tabl, column, by="GENES", all=TRUE)
  }
}

head(snvm_tabl, 10)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(snvm_tabl[,3])))
#check that the 1s are in the correct place
dim(snvm_tabl)
snvm_tabl[which(snvm_tabl[,5]==1),]
class(snvm_tabl)
snvm_tabl <- as.data.frame(snvm_tabl)
saveRDS(snvm_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/snvm_table.Rds")
```
 #SNVLow pass
```{r}
#Making the table
options(stringsAsFactors = FALSE)
genelist_snvl <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvl.Rds")
#snvl_tabl <- as.data.frame(rep(0,nrow(genelist_snvl)), row.names =genelist_snvl)
toy_snvl <-files_snvl[1:10]
#defining Temp outside of the function to prevent it's repeated emptying
temp <- genelist_snvl
snvl_tabl <- temp
x <- files_snvl[388]
for (i in 1:length(files_snvl)){
  x<- files_snvl[i]
  base <- tools::file_path_sans_ext(basename(x))
  base <- gsub("_pSNVLOW","",base)
  named_snvl <- c(base,"genes")
   if (file.size(x)>0){
    #print(named)
    #save each table as a rds then red it back in as a dataframe with column names
    mini_table <- read.table(x, header =FALSE, fill = TRUE)
    
    sum(mini_table[,1])
    if(mini_table[1,2] == ""){
          mini_table <- mini_table[2:nrow(mini_table),]
        }
    colnames(mini_table) <- named_snvl
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    snvl_tabl <- merge(snvl_tabl, column, by= "GENES", all=TRUE)
    head(snvl_tabl)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named_snvl
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    snvl_tabl <- merge(snvl_tabl, column, by="GENES", all=TRUE)
  }
}

head(snvl_tabl)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(snvl_tabl[,389])))
#check that the 1s are in the correct place
dim(snvl_tabl)
snvl_tabl[which(snvl_tabl[,5]==1),]
class(snvl_tabl)
snvl_tabl <- as.data.frame(snvl_tabl)
saveRDS(snvl_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/snvl_table.Rds")
```
#Indel Section
```{r}
#Making the table
options(stringsAsFactors = FALSE)
genelist_IDH <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
#IDH_tabl <- as.data.frame(rep(0,nrow(genelist_IDH)), row.names =genelist_IDH)
toy_IDH <-files_IDH[1:10]
#defining Temp outside of the function to prevent it's repeated emptying
temp <- genelist_IDH
IDH_tabl <- temp
#TEST:x <- files_IDH[5]
for (i in 1:length(files_IDH)){
  x<- files_IDH[i]
  base <- tools::file_path_sans_ext(basename(x))
  base <- gsub("_pINDELHIGH","",base)
  named_IDH <- c(base,"genes")
   if (file.size(x)>0){
    #print(named)
    #save each table as a rds then red it back in as a dataframe with column names
    mini_table <- read.table(x, header =FALSE, fill = TRUE)
   # TEST:sum(mini_table[,1])
    if(mini_table[1,2] == ""){
          mini_table <- mini_table[2:nrow(mini_table),]
        }
    colnames(mini_table) <- named_IDH
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    IDH_tabl <- merge(IDH_tabl, column, by="GENES", all=TRUE)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named_IDH
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    IDH_tabl <- merge(IDH_tabl, column, by="GENES", all=TRUE)
  }
}

head(IDH_tabl, 10)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(IDH_tabl[,6])))
#check that the 1s are in the correct place
dim(IDH_tabl)
IDH_tabl[which(IDH_tabl[,5]!=0),]
class(IDH_tabl)
IDH_tabl <- as.data.frame(IDH_tabl)
saveRDS(IDH_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/IDH_table.Rds")
```

#INDEL MODIFIERS
```{r}
#Making the table
options(stringsAsFactors = FALSE)
#Only run if starting here: genelist_IDM <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
#IDM_tabl <- as.data.frame(rep(0,nrow(genelist_IDM)), row.names =genelist_IDM)
toy_IDM <-files_IDM[1:10]
#defining Temp outside of the function to prevent it's repeated emptying
temp <- genelist_IDM
IDM_tabl <- temp
#x <- files_IDM[534]
for (i in 1:length(files_IDM)){
  x<- files_IDM[i]
  base <- tools::file_path_sans_ext(basename(x))
  named_IDM <- c(base,"genes")
   if (file.size(x)>0){
    mini_table <- read.table(x, header =FALSE, fill = TRUE)
   #sum(mini_table[,1])
   #head(mini_table)
    if(mini_table[1,2] == ""){
          mini_table <- mini_table[2:nrow(mini_table),]
        }
    colnames(mini_table) <- named_IDM
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    IDM_tabl <- merge(IDM_tabl, column, by="GENES", all=TRUE)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named_IDM
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    IDM_tabl <- merge(IDM_tabl, column, by="GENES", all=TRUE)
  }
}

head(IDM_tabl, 10)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(IDM_tabl[,535])))
#check that the 1s are in the correct place
dim(IDM_tabl)
IDM_tabl[which(IDM_tabl[,5]!=0),]
class(IDM_tabl)
#IDM_tabl <- as.data.frame(IDM_tabl)
saveRDS(IDM_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/IDM_table.Rds")
```

#INDEL LOW
```{r}

#Making the table
options(stringsAsFactors = FALSE)
#Only run if starting here: genelist_IDL <- readRDS("/Volumes/home/greally-lab/T_Trial/Tables/genelist_snvh.Rds")
#IDL_tabl <- as.data.frame(rep(0,nrow(genelist_IDL)), row.names =genelist_IDL)


#stopped here - RUN TOY DATA
toy_IDL <-files_IDL[1:10]
#defining Temp outside of the function to prevent it's repeated emptying
temp <- genelist_IDL
IDL_tabl <- temp
x <- files_IDL[42]
for (i in 1:length(files_IDL)){
  x<- files_IDL[i]
  base <- tools::file_path_sans_ext(basename(x))
  named_IDL <- c(base,"genes")
   if (file.size(x)>0){
    mini_table <- read.table(x, header =FALSE, fill = TRUE)
   sum(mini_table[,1])
   #head(mini_table)
    if(mini_table[1,2] == ""){
          mini_table <- mini_table[2:nrow(mini_table),]
        }
    colnames(mini_table) <- named_IDL
    column <- merge(temp,mini_table, by.x = "GENES",by.y="genes", all=TRUE)
    column[is.na(column)] <- 0
    IDL_tabl <- merge(IDL_tabl, column, by="GENES", all=TRUE)
}
  else{
    empty_table <- cbind(rep(0,nrow(temp)), temp)
    #head(empty_table)
    colnames(empty_table)<-named_IDL
    column <- merge(temp,empty_table, by.x = "GENES",by.y="genes",all = TRUE)
    IDL_tabl <- merge(IDL_tabl, column, by="GENES", all=TRUE)
  }
}

head(IDL_tabl, 10)
#check that the second pt column has 11 1s in it
sum(as.numeric(as.character(IDL_tabl[,43])))
#check that the 1s are in the correct place
dim(IDL_tabl)
IDL_tabl[which(IDL_tabl[,5]!=0),]
class(IDL_tabl)
#IDL_tabl <- as.data.frame(IDL_tabl)
saveRDS(IDL_tabl, file = "/Volumes/home/greally-lab/T_Trial/Tables/IDL_table.Rds")
```

#testing to see what output I get from reading in each file
```{r}
  b <- read.table("/Volumes/home/greally-lab/T_Trial/Tables/0189de34-fb68-471f-b0bd-e9a27bfaa3c4_pSNVHIGH.txt", header = F)
  #make that matrix entry = [match,x] set that equal to x$v1[i] else set equal to 0
  snvh_tab <- cbind(genelist,0)
  snvh_table <- genelist
```
  #This is the code I used to make each column for the matrix      

  
```{r}
    for (i in 1:length(b$V2)){
    c <- b$V2[i]
    match <- charmatch(c,snvh_table)
     print(match)
     #print(b)
     snvh_tab[match,2] <- b$V1[i]
    }
    colnames(snvh_tab)[,2] <- "burrito""
     new_row <- as.matrix(snvh_tab[,"burrito""])
     View(new_row)
    
      #for(j in 1:length(match))
      #{
      #if(snvh_table==match[j]){
      #snvh_tab[match,2] <- b$V1[i]}
        #else{
        #snvh_tab[,2] = 0
        #}
      
  }
    matchb <- charmatch(b$v2,snvh_table$V1)
    
    
 #t <- read.table(x, header=F)
 #colnames(t) <- c("counts", basename)
 #create a table of all the gene names
   #if(t(!duplicated(t$basename))){ 
   #}
   
butt_2 <- b$head
monkey <-as.vector(b$bitch)
monkeybutt <-table(monkey,butt)
View(monkeybutt)
colnames(b) <- c("head","bitch")
monkey_2 <-monkey[!duplicated(monkey)]
View(monkey)
```

 ## Including Plots

```{r pressure, echo=FALSE}
 
```

 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 